---
title: "Graph for data science module 4"
categories: 
  - "Data Sciences I"
description: 
  "The selected dataset is urchin_bio. It is a dataset of sea urchins biometry that shows several features from *Paracentrotus lividus* who have been sinned in Brittany or in urchins farm in Normandy."
author:
  - name: De Tandt Bastien
    url: {}
date: "`November 10, 2020`"
#preview: 
output:
  distill::distill_article:
    self_contained: false
---

```{r setup}
SciViews::R
```

```{r}
urchin <- read("urchin_bio", package = "data.io")
urchin <- drop_na(urchin_bio)
?urchin_bio
```

```{r}
chart(data = urchin, as.numeric(weight) ~ as.numeric(height) %col=% origin) + 
  geom_point() +
  geom_line() +
  labs(x = "height (in mm)", y = "weight (in g)")
```

This graphic shows two things. The first one is that the height and the weight are correletad and the second one is that the origin of the urchins has an impact on these two factors.The farm urchins can reach higher height and weight.

```{r}
group_by(urchin, maturity) %>.%
  summarise(., mean = mean(height)) -> urchin1

ggplot(urchin1, aes(x = maturity, y = mean)) +
  geom_point() + 
  geom_segment( aes(x = maturity, xend = maturity, y = 0, yend = mean)) +
  labs(x = "Gonads maturity", y = "average height (mm)" )
```

This graphic shows that the level of gonads maturity has no impact on the average height of the urchin.

```{r}
ggplot(urchin, aes(x = spines, y = height)) +
  geom_area(na.rm = TRUE, position = "dodge")
```

We can see here that more the height of the test is high, more dry weight of calcareous parts of the spines is high too.
