---
title: "Graph for data science module 4"
categories: 
  - "Data Sciences I"
description: 
  "The selected dataset is urchin_bio. It is a dataset of sea urchins biometry that shows several features from *Paracentrotus lividus* who have been sinned in Brittany or in urchins farm in Normandy."
author:
  - name: De Tandt Bastien
    url: {}
date: "`November 10, 2020`"
#preview: 
output:
  distill::distill_article:
    self_contained: false
---

```{r setup}
SciViews::R
```

```{r}
data <- read("urchin_bio", package = "data.io")
```

```{r}
?urchin_bio
```

```{r}
height <- 0:3
digestive_tract <- cumsum(rnorm(4))
urchin_bio <- data.frame(height, digestive_tract)
  ggplot(data, aes(x = height, y = digestive_tract)) +
  geom_line(na.rm = TRUE)
```

By relating the weight of the digestive tract in y to the size in x, the graph shows that there is some correlation between these two factors. When the height increases, the weight of the digestive tract increases too.

```{r}
ggplot(data, aes(x = origin, y = skeleton)) + 
geom_point(aes(color = origin), na.rm = TRUE) +
geom_segment(aes(x = origin, xend = origin, y = 0,  yend = skeleton, color = origin), na.rm = TRUE)
```

With this graph, we can see that the origin of the animal have an impact on the weight of the skeleton, the urchin from a farm have a heavier skeleton.

```{r}
ggplot(data, aes(x = spines, y = height)) +
  geom_area(na.rm = TRUE, position = "dodge")
```

We can see here that more the height of the test is high, more dry weight of calcareous parts of the spines is high too.
